A 3d curvilinear skeletonization algorithm with application to path tracing

### 2012-09-14 application_to_path_tracing.tex
Test

\subsection{Results and discussion}

Some results are presented on Fig.~\ref{fig:results} and Fig.~\ref{fig::intro_image} where we can see that our method produce less noisy images compared to the regular path tracing. We present, in table~\ref{tab:timing}, the time taken by each method to produce an image of same quality (the quality is measured by the mean square error (MSE) with a reference image) in different scenes.

>>>>

\subsection{Results and discussion}
Some results are presented on Fig.~\ref{fig:results} and Fig.~\ref{fig::intro_image} where we can see that our method produce less noisy images compared to the regular path tracing. We present, in table~\ref{tab:timing}, the time taken by each method to produce an image of same quality (the quality is measured by the mean square error (MSE) with a reference image) in different scenes.
